Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2020-01-23 paper/manuscript.tex
updatng figure for convergence

    The top panel shows the three-step protocol for a perturbation involving 5 perturbed atoms, while the bottom panel shows the same protocol for a perturbation involving 10 perturbed atoms. The difference in energy between the forward (blue) and reverse (red) free energy calculations at the midpoint of the simulation time gives an indication of the overall convergence of the simulation, with differences over 1 k$_{B}$T indicating poor convergence.}

>>>>

    Subplots \textbf{A}, \textbf{C}, and \textbf{E} show a three step protocol  for a perturbation involving 3 perturbed atoms, while \textbf{B}, \textbf{D}, and \textbf{F} shows the same protocol for a perturbation involving 10 perturbed atoms. The first step of the protocol is the recharging then removing van der Waals interactions and then recharging. The difference in energy between the forward (blue) and reverse (red) free energy calculations at the midpoint of the simulation time gives an indication of the overall convergence of the simulation, with differences over 1 k$_{B}$T indicating poor convergence.}
